---
title: "A Demo for the Github Distill page"
description: |
  In this demo I will be making some plots using the Iris data set -- a boxplot and a scatter plot
author:
  - name: Nathan Nguyen
    url: {}
date: 05-15-2021
output:
  distill::distill_article:
    self_contained: false
    code_folding: 'hide'
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
#Attach packages
library(tidyverse)
library(here)
library(stargazer)
library(naniar)
library(broom)
library(ggsci)
```


# Overview

This report will be a demo for the website that I am working on. This will just demonstrate my basic capabilities with the ggplot2 library by constructing a boxplot and a scatterplot with multiple linear models.

- exploring ggplot
- making the code folds work
- attempting to get this to run on the Github website

```{r}
getdata <- function(...){
  e = new.env()
  name = data(..., envir = e)[1]
  e[[name]]
}

data <- getdata("iris")
```

# The boxplot

### Sepal Length Boxplot by Species

- color indicates which species

```{r, message = FALSE, warning = FALSE}
data %>%
  ggplot(aes(x = Species, y = Sepal.Length, fill = Species)) +
  geom_boxplot(aes(group = Species)) +
  labs(x = "Species",
       y = "Sepal Length",
       title = "Sepal Length Box Plot by Species") +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = "none") +
  scale_fill_d3()
```

### The scatterplot and linear models by species

- color indicates species

```{r, message = FALSE, warning = FALSE}
data %>%
  ggplot(aes(x = Sepal.Length, y = Sepal.Width, color = Species)) +
  geom_point(aes(group = Species)) + geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Sepal Length",
       y = "Sepal Width",
       title = "Sepal Width Function of Sepal Length") +
  scale_color_d3() +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = "top")
```

```{r, include = FALSE}
lm1 <- lm(Sepal.Length ~ Species + Sepal.Width, data = data)
```


# Stargazer Table

```{r, message = FALSE, warning = FALSE, echo = FALSE, results = 'asis'}
stargazer(lm1, type = "html",
          covariate.labels = c("Versicolor", "Virginica", "Sepal Width"),
          dep.var.labels = "Sepal Length")

```